Sumbission Steps

### 2020-09-16 code/03-submission-steps.Rmd
small changes

**NOTE** The knitr option of `eval = FALSE` has been set for this document, so all code must be run manually from withing the Rmd file. This is done to be safe about not deleting or replacing files.

@@

1. Delete all files generated by `paper.Rnw` and current existing submission folder using the code below.

    ```{r}
    # Individual files to delete
    file.remove("../data/bullet-explain.rds")
    file.remove("../data/bullet-lime.rds")
    file.remove("../data/sine-lime-explain.rds")
    file.remove("../figure-static/figure-10-1.eps")
    file.remove("../figure-static/figure-10-1.png")

@@

2. Knit the file `paper.Rnw`.

3. Run the following code to move all files necessary to the submission folder.

@@

4. Manually delete `figure/` and `figure-static/` from the figure file paths in `paper.tex`. For example, change `\includegraphics[width=6.5in]{figure/figure-01-1}` to `\includegraphics[width=6.5in]{figure-01-1}`.

5. Compile the file `paper.tex` (using LaTex, then bibTex, then LaTeX twice more) to make sure it compiles correctly (especially references).

6. Besides for `paper.pdf`, delete all other files generated when `paper.tex` was compiled. This includes other paper files and pdf versions of the figures.

@@

7. Upload all remaining files in the submission folder to the ASA Data Science Journal submission page which should be:

>>>>

**NOTE** The knitr option of `eval = FALSE` has been set for this document, so all code must be run manually from within the Rmd file. This is done to be safe about not deleting or replacing files.

@@

1. Delete all data files created from the raw versions, files generated by `paper.Rnw`, and current existing submission folder using the code below.

    ```{r}
    # Individual files to delete
    file.remove("../data/bullet-explain.rds")
    file.remove("../data/bullet-lime.rds")
    file.remove("../data/bullet-rf.rds")
    file.remove("../data/bullet-test.csv")
    file.remove("../data/bullet-test.csv.zip")
    file.remove("../data/bullet-train.csv")
    file.remove("../data/bullet-train.csv.zip")
    file.remove("../data/example-signatures.csv")
    file.remove("../data/example-signatures.csv.zip")
    file.remove("../data/sine-lime-explain.rds")
    file.remove("../figure-static/figure-08-1.eps")
    file.remove("../figure-static/figure-08-1.png.zip")
    file.remove("../figure-static/figure-10-1.eps")
    file.remove("../figure-static/figure-10-1.png")

@@

2. Manually run the code in `code/01-raw-file-compression.Rmd` to compress the raw versions of the data files and static figure. Also, knit the file to make sure the html version is up to date.

3. Manually run the code in `code/02-data-preparation.Rmd` to create the versions of the data to be used in the manuscript and submitted with the manuscript. Also, knit the file to make sure the html version is up to date.

4. Knit the file `paper.Rnw`.

5. Run the following code to move all files necessary to the submission folder.

@@

6. Manually delete `figure/` and `figure-static/` from the figure file paths in `paper.tex`. For example, change `\includegraphics[width=6.5in]{figure/figure-01-1}` to `\includegraphics[width=6.5in]{figure-01-1}`.

7. Compile the file `paper.tex` (using LaTex, then bibTex, then LaTeX twice more) to make sure it compiles correctly (especially references).

8. Besides for `paper.pdf`, delete all other files generated when `paper.tex` was compiled. This includes other paper files and pdf versions of the figures.

@@

9. Upload all remaining files in the submission folder to the ASA Data Science Journal submission page which should be:
